|

### 2022-02-04 publication/supplementary_material.Rmd
add author and journal information to supplementary materials document

---
title: |
  | Supplementary Material\:
  | Regularized target encoding outperforms traditional methods in supervised machine learning with high cardinality features
numbersections: true
csl: elsevier-harvard.csl
bibliography: literature.bib
output: pdf_document
header-includes:
   - \usepackage{algorithm}
   - \usepackage{array}
   - \usepackage[noend]{algpseudocode}
   - \usepackage{amsmath}
   - \usepackage{amssymb}
   - \usepackage{amsfonts}
   - \usepackage{mathtools}
   - \usepackage{bm}
   - \usepackage{tikz}
   - \usepackage{threeparttable}
   - \usepackage{booktabs}
   - \usetikzlibrary{trees,arrows, chains, fit, positioning, calc, shapes, shadows}
   - \setlength\parindent{0pt}
   - \usepackage{pdflscape}
   - \usepackage{float}
---

@@

Feature encoding techniques are implemented in several general preprocessing packages.
We provide an overview of existing implementations for R in Table \ref{tab:impls}.
For python, an extension to scikit-learn [@pedregosa_2011], *category encoders* [@will_mcginnis_2018_1157110] is available.
To enable a fair and reliable comparison in our study, we implemented all methods outlined above on top of the `mlrCPO` package.
All code can be found in our **online repository** (<https://github.com/compstat-lmu/paper_2021_categorical_feature_encodings>).

@@

*Note on GLMM Encoders:* To speed up the computation of the GLMM encoders, we followed the performance tips from the lme4 vignette (<https://cran.r-project.org/web/packages/lme4/vignettes/lmerperf.html>): we did not compute derivations (`calc.derivs = FALSE`) and used the `NLOPT_LN_BOBYQA` optimizer from the nloptr package with liberal stopping criteria (`maxeval = 1000`, `xtol_abs = 1e-6`, `ftol_abs = 1e-6`).

@@

A frequently asked question is, whether one-hot encoding or dummy encoding is to be preferred. While dummy encoding clearly is commonly preferred for non-regularized linear models, the answer is less clear for general machine learning algorithms studied in our setting.

@@

From the results shown in Table \ref{tab:oneh-win} we can observe, that for most algorithms and datasets, one-hot encoding is to be preferred over dummy-encoding.

>>>>

---
title: |
  | Supplementary Material\:
  | Regularized target encoding outperforms traditional methods in supervised machine learning with high cardinality features
author:
  - Florian Pargent
  - Florian Pfisterer
  - Janek Thomas
  - Bernd Bischl
subtitle: Published in Computational Statistics
numbersections: true
csl: elsevier-harvard.csl
bibliography: literature.bib
output: pdf_document
header-includes:
   - \usepackage{algorithm}
   - \usepackage{array}
   - \usepackage[noend]{algpseudocode}
   - \usepackage{amsmath}
   - \usepackage{amssymb}
   - \usepackage{amsfonts}
   - \usepackage{mathtools}
   - \usepackage{bm}
   - \usepackage{tikz}
   - \usepackage{threeparttable}
   - \usepackage{booktabs}
   - \usetikzlibrary{trees,arrows, chains, fit, positioning, calc, shapes, shadows}
   - \setlength\parindent{0pt}
   - \usepackage{pdflscape}
   - \usepackage{float}
---

@@

Feature encoding techniques are implemented in several general preprocessing packages.
We provide an overview of existing implementations for R in Table \ref{tab:impls}.
For python, an extension to `scikit-learn` [@pedregosa_2011], *category encoders* [@will_mcginnis_2018_1157110] is available.
To enable a fair and reliable comparison in our study, we implemented all methods outlined above on top of the `mlrCPO` package.
All code can be found in our **online repository** (<https://github.com/compstat-lmu/paper_2021_categorical_feature_encodings>).

@@

*Note on GLMM Encoders:* To speed up the computation of the GLMM encoders, we followed the performance tips from the `lme4` vignette (<https://cran.r-project.org/web/packages/lme4/vignettes/lmerperf.html>): we did not compute derivations (`calc.derivs = FALSE`) and used the `NLOPT_LN_BOBYQA` optimizer from the `nloptr` package with liberal stopping criteria (`maxeval = 1000`, `xtol_abs = 1e-6`, `ftol_abs = 1e-6`).

@@

A frequently asked question is whether one-hot encoding or dummy encoding is to be preferred. While dummy encoding clearly is commonly preferred for non-regularized linear models, the answer is less clear for general machine learning algorithms studied in our setting.

@@

From the results shown in Table \ref{tab:oneh-win} we can observe that for most algorithms and datasets, one-hot encoding is to be preferred over dummy-encoding.
